---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# musicvisualizer

<!-- badges: start -->
[![R-CMD-check](https://github.com/HualongXu/musicvisualizer/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/HualongXu/musicvisualizer/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The `musicvisualizer` package retrieves and filters data that contains [an album's features](https://spotify.com) from Spotify. It displays all these features in one plot.

## Installation

You can install the development version of musicvisualizer from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("HualongXu/musicvisualizer")
```

## Visualize Album's Features

Given an artist's name and ONE of their album's name, the `musicvisualizer()` function retrieves a raw data that is later filtered down to five features (energy, danceability, valence, instrumentalness, acousticness) for the album.

```{r example}
library(musicvisualizer)
##basic example code

first_musicvisualizer <- musicvisualizer("Olivia Rodrigo", "GUTS")
first_musicvisualizer
```

We can plot them in one visualization to see the album's tendency in energy, danceability, valence, and acousticness.

```{r}
plot(first_musicvisualizer)
```

