---
title: "Intro_musicvisualizer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro_musicvisualizer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(musicvisualizer)
```

# musicvisualizer

<!-- badges: start -->

<!-- badges: end -->

The `musicvisualizer` package retrieves and filters data that contains [an album's features](https://spotify.com) from Spotify. It displays all these features in one plot.

## Visualize Album's Features

Given an artist's name and ONE of their album's name, the `musicvisualizer()` function retrieves a raw data that is later filtered down to five features (energy, danceability, valence, instrumentalness, acousticness) for the album.

```{r example}
library(musicvisualizer)
##basic example code

first_musicvisualizer <- musicvisualizer("Olivia Rodrigo", "GUTS")
first_musicvisualizer
```

We can plot them in one visualization to see the album's tendency in energy, danceability, valence, and acousticness.

```{r}
plot(first_musicvisualizer)
```

**A thorough example via Midnights by Taylor Swift**
```{r}
midnights_musicvisualizer <- musicvisualizer("Taylor Swift", "Midnights")
midnights_musicvisualizer

plot(midnights_musicvisualizer)
```


## Features Data

The metadata is aggregated into `musicvisualizer_data`

```{r}
head(musicvisualizer_data)
```


**How many songs are in each of the artist's albums?**

```{r}
library(dplyr)
library(ggplot2)
```

```{r}
musicvisualizer_songs_count <- musicvisualizer_data |>
  group_by(album_name) |>
  summarize(songs_count = n())
```

```{r}
ggplot(data = musicvisualizer_songs_count,
       aes(x = album_name, y = songs_count)) +
  geom_col()
```
